\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-08 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

With step size $h=10^{-3}$, we discretized time $t\in[0,1]$. Using Algorithm \ref{algo:KineticProx}, we propagated $N=1000$ random samples from \eqref{rho0IEEE14}, and evaluated at \eqref{rho0IEEE14}, to update the scattered weighted point clouds $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ over $\mathbb{T}^{5}\times\mathbb{R}^{5}$ at times $t_{k}:=kh$, $k\in\mathbb{N}$. We used the algorithmic parameters $\varepsilon=0.05$, $\delta=10^{-3}$, $L=300$.

Fig. \ref{fig:IEEE14marginals} shows the time snapshots of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs for generator $i=1,\hdots, n=5$, computed using the weighted point clouds $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$. Notice that in Fig. \ref{fig:IEEE14marginals}, the horizontal axes of the subfigures have periodic boundary conditions, i.e., $(\theta_{i},\omega_{i})\in\mathbb{T}\times\mathbb{R}$ (cylinder). Fig. \ref{fig:CompTimeIEEE14bus} shows the computational times needed to update $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ via Algorithm \ref{algo:KineticProx}.

>>>>

With step size $h=10^{-3}$, we discretized time $t\in[0,1]$. Using the Euler-Maruyama scheme and the Algorithm \ref{algo:KineticProx}, we propagated $N=1000$ random samples from \eqref{rho0IEEE14}, and evaluated at \eqref{rho0IEEE14}, to update the scattered weighted point clouds $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ over $\mathbb{T}^{5}\times\mathbb{R}^{5}$ at times $t_{k}:=kh$, $k\in\mathbb{N}$. We used the algorithmic parameters $\varepsilon=0.05$, $\delta=10^{-3}$, $L=300$.

Fig. \ref{fig:IEEE14marginals} shows the time snapshots of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs for generator $i=1,\hdots, n=5$, computed using the weighted point clouds $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$. Notice that in Fig. \ref{fig:IEEE14marginals}, the horizontal axes of the subfigures have periodic boundary conditions, i.e., $(\theta_{i},\omega_{i})\in\mathbb{T}\times\mathbb{R}$ (cylinder). Fig. \ref{fig:CompTimeIEEE14bus} shows the computational times needed to update $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ via the Euler-Maruyama and the Algorithm \ref{algo:KineticProx}.
